\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist,url}
\usepackage[margin=1in]{geometry}

\theoremstyle{definition}
\newtheorem*{problem}{Problem}
\newtheorem*{solution}{Solution}

\begin{document}


% Chapter 1.1, Problem 1
\begin{problem}[Rosen.1.1.7]\ \\
\ \\
Suppose that during the most recent fiscal year, the annual
revenue of Acme Computer was 138 billion dollars
and its net profit was 8 billion dollars, the annual revenue
of Nadir Software was 87 billion dollars and its net profit
was 5 billion dollars, and the annual revenue of Quixote
Media was 111 billion dollars and its net profit was
13 billion dollars. Determine the truth value of each of
these propositions for the most recent fiscal year.
\ \\
\begin{compactenum}
\renewcommand{\theenumi}{\alph{enumi}}
\item Quixote Media had the largest annual revenue.
\item Nadir Software had the lowest net profit and Acme
Computer had the largest annual revenue.
\item Acme Computer had the largest net profit or Quixote
Media had the largest net profit.
\item If Quixote Media had the smallest net profit, then
Acme Computer had the largest annual revenue.
\item Nadir Software had the smallest net profit if and only
if Acme Computer had the largest annual revenue

\end{compactenum}
\end{problem}

\begin{solution}\ \\
\ \\
\noindent 
\textit{Propositions}:\ \\
p: The annual revenue of Acme Computer was 138 billion dollars and its net profit was 8 billion dollars\ \\
q: The annual revenue of Nadir Software was 87 billion dollars and its net profit
was 5 billion dollars\ \\
r: The annual revenue of Quixote Media was 111 billion dollars and its net profit was
13 billion dollars\ \\
\begin{compactenum}
\renewcommand{\theenumi}{\alph{enumi}}
\item This statement is false.
\item Propositions $p \wedge q$ where p is true and q is true. $T \wedge T \equiv T$. $\therefore$ True
\item Propositions $p \vee q$ where p is false and q is true. $F \vee T \equiv T$. $\therefore$ True
\item Propositions $p \xrightarrow{} q$ where p is false and q is true. $T \xrightarrow{} F \equiv T$. $\therefore$ True
\item Propositions $p \leftrightarrow q$ where p is true and q is true. $T \leftrightarrow T \equiv T$. $\therefore$ True
\end{compactenum}
\end{solution}

\end{document}