\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist,url}
\usepackage[margin=1in]{geometry}

\theoremstyle{definition}
\newtheorem*{problem}{Problem}
\newtheorem*{solution}{Solution}

\begin{document}


% Chapter 1.1, Problem 1
\begin{problem}[Rosen.1.1.9]\ \\
Let p and q be the propositions “Swimming at the New
Jersey shore is allowed” and “Sharks have been spotted
near the shore,” respectively. Express each of these compound
propositions as an English sentence.
\begin{compactenum}
\renewcommand{\theenumi}{\alph{enumi}}
\item $\neg q$ 
\item $p \wedge q$ 
\item $\neg p \vee q$
\item $p \rightarrow \neg q$ 
\item $\neg q \rightarrow p$ 
\item $\neg p \rightarrow \neg q$
\item $p \leftrightarrow \neg q$ 
\item $\neg p \wedge (p \vee \neg q)$
\end{compactenum}
\end{problem}
\begin{solution}\ \\

\begin{compactenum}
\renewcommand{\theenumi}{\alph{enumi}}
\item Sharks have not been spotted near the shore.
\item Swimming at the new jersey shore is allowed and sharks have been spotted near the shore.
\item Swimming at the new jersey shore is not allowed or sharks have been spotted near the shore.
\item If swimming at the new jersey shore is allowed then sharks have note been spotted near the shore.
\item If sharks have not been spotted near the shore then swimming at the new jersey shore is allowed.
\item If swimming at the new jersey shore is not allowed, then sharks have been spotted near the shore.
\item Swimming at the new jersey shore is allowed if and only if sharks have been spotted near the shore.
\item Swimming at the new jersey shore is not allowed and, swimming is allowed at the new jersey shore or sharks have note been spotted near the shore.
\end{compactenum}
\end{solution}

\end{document}