\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist,url}
\usepackage[margin=1in]{geometry}

\theoremstyle{definition}
\newtheorem*{problem}{Problem}
\newtheorem*{solution}{Solution}

\begin{document}

% Hunter Cleary
% Chapter 1.2, Problem 38
\begin{problem}[Rosen.1.2.38]\ \\
\ \\
Solve this famous logic puzzle, attributed to Albert Einstein,
and known as the zebra puzzle. Five men with
different nationalities and with different jobs live in consecutive
houses on a street. These houses are painted different
colors. The men have different pets and have different
favorite drinks. Determine who owns a zebra and
whose favorite drink is mineral water (which is one of the
favorite drinks) given these clues: The Englishman lives
in the red house. The Spaniard owns a dog. The Japanese
man is a painter. The Italian drinks tea. The Norwegian
lives in the first house on the left. The green house is
immediately to the right of the white one. The photographer
breeds snails. The diplomat lives in the yellow house.
Milk is drunk in the middle house. The owner of the green
house drinks coffee. The Norwegian’s house is next to the
blue one. The violinist drinks orange juice. The fox is in
a house next to that of the physician. The horse is in a
house next to that of the diplomat. [Hint: Make a table
where the rows represent the men and columns represent
the color of their houses, their jobs, their pets, and their
favorite drinks and use logical reasoning to determine the
correct entries in the table.]\ \\
\begin{compactenum}
\renewcommand{\theenumi}{\alph{enumi}}
\end{compactenum}
\end{problem}

\begin{solution}\ \\
\ \\
\textit{Statements}:\ \\
\ \\
(1) The Englishmen lives in the red house.\ \\
(2) The Spaniard owns a dog.\ \\
(3) The Japanese man is a painter.\ \\
(4) The Italian drinks tea.\ \\
(5) The Norwegian lives in the first house on the left.\ \\
(6) The green house is immediately to the right of the white one.\ \\
(7) The photographer breeds snails.\ \\
(8) The diplomat lives in the yellow house.\ \\
(9) Milk is drunk in the middle house.\ \\
(10) The owner of the green house drinks coffee.\ \\
(11) The Norwegian’s house is next to the blue one.\ \\
(12) The violinist drinks orange juice.\ \\
(13) The fox is in a house next to that of the physician.\ \\
(14) The horse is in a house next to that of the diplomat.\ \\
\ \\
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Table of Radical Wacky Houses :0 woah!}
  \ \\
    \begin{tabular}{llllll}
    House & \multicolumn{1}{r}{1} & \multicolumn{1}{r}{2} & \multicolumn{1}{r}{3} & \multicolumn{1}{r}{4} & \multicolumn{1}{r}{5} \\
    Color & Yellow & Blue  & Red   & Ivory & Green \\
    Nationality & Norwegian & Italian & Englishman & Spainiard & Japanese \\
    Drink & Water & Tea   & Milk  & O.J.  & Coffee \\
    Pet   & Fox   & Horse & Snails & Dog   & Zebra \\
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%

\ \\
The Japanese man owns the zebra.\ \\ 
The Norwegian drinks water.\ \\ % stay thirsty my friends :-D
\ \\


\begin{compactenum}
\renewcommand{\theenumi}{\alph{enumi}}  





\end{compactenum}
\end{solution}

\end{document}